### 2021-03-05 2021.csic5011/homework/homework04.tex
Add files via upload

\lecture{Homework 4. Random Projections}{Yuan Yao}{Due: in 1.5 weeks}{Mar. 11, 2020}

@@

Can you try to give an analysis of the phenomenon observed? Tropp's paper mentioned on class may give you a good starting point.

>>>>

\lecture{Homework 4. Random Projections}{Yuan Yao}{Due: in 1 week}{March 5, 2021}

@@

Can you try to give an analysis of the phenomenon observed? The following paper by Tropp et al. may give you a good starting point to think.

\begin{itemize}
\item Dennis Amelunxen, Martin Lotz, Michael B. McCoy, Joel A. Tropp. Living on the edge: Phase transitions in convex programs with random data. arXiv:1303.6672. URL: \url{https://arxiv.org/abs/1303.6672} 
\end{itemize}
